Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-03-10 reports/manuscript_papaja.Rmd
Second pass of comments
Add single rmd for manuscript

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : yes

@@

# Uncomment to run outside of pipeline
library(tidyverse)
library(targets)
library(xfun)
```

```{r child = 'manuscript_content.Rmd'}

```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

# Uncomment to run outside of pipeline
library(tidyverse)
library(targets)
library(xfun)
library(DiagrammeR)
library(gt)
```

```{r child = 'manuscript_content.Rmd'}
```
